%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Platform Engineer Lead \& Site Reliability Engineer} % Job title
    {Stratio BD} % Organization
    {Madrid, Spain} % Location
    {Sep. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team to automate deployment and management of Kubernetes clusters across major cloud providers (Azure, AWS, GCP), and on-premise environments, optimizing efficiency and scalability.}
        \item {Designed scalable and resilient platform architectures, adhering to industry standards and security practices.}
        \item {Utilized Ansible, Terraform, Helm, and custom Kubernetes operators for provisioning, deployment, and automation of complex workflows.}
        \item {Integrated cutting-edge technologies such as Ingress Controller, OAuth2 proxy, Vault, and various Kubernetes storage providers to enhance platform robustness.}
        \item {Collaborated with stakeholders to implement observability components like Prometheus, Grafana and EFK stack for monitoring and logging.}
        \item {Investigated and resolved issues across platform technologies, documenting findings and implementing proactive measures to enhance cluster resilience.}
        \item {Guided clients in Kubernetes adoption, tailoring solutions to meet specific business requirements.}
        \item {Actively contributed to open-source projects like Kubespray, fostering collaboration and innovation within the Kubernetes ecosystem.}
      \end{cvitems}
    }

  \cventry
    {Platform Engineer \& DevOps Engineer} % Job title
    {Stratio BD} % Organization
    {Madrid, Spain} % Location
    {Sep. 2014 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed automation solutions for deploying and managing Mesos clusters, improving operational efficiency.}
        \item {Integrated technologies like Etcd, Vault, and Consul to enhance functionality and security of Mesos clusters.}
        \item {Provided expertise in Mesos adoption, platform optimization, and customization for client needs.}
        \item {Cultivated a collaborative environment within the team, driving innovation and continuous improvement initiatives.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Game Developer} % Job title
    {Wayra. Telefónica} % Organization
    {Madrid, Spain} % Location
    {Jul. 2013 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created cross-platform mobile games for a top retail brand using Unity, ensuring seamless gameplay across iOS and Android devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
