%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ESG \& Engagement Specialist} % Job title
    {Stratio BD} % Organization
    {Madrid, Spain} % Location
    {2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded ESG initiatives targeting environmental sustainability, social responsibility, and governance practices.}
        \item {Implemented programs driving environmental sustainability, social responsibility, and governance objectives.}
        \item {Contributed to policy development aligning business objectives with ethical and sustainable practices.}
        \item {Designed and executed engagement strategies fostering organizational cohesion.}
        \item {Negotiated, designed, and implemented equality and diversity policies ensuring compliance.}
        \item {Collaborated with foundations to uphold diversity policies.}
        \item {Transparently reported progress on ESG initiatives.  }
        \item {Crafted global policies promoting Diversity, Sustainability, and Well-being, establishing a robust framework for organizational success.}
      \end{cvitems}
    }

   \cventry
    {Culture and Talent Developer} % Job title
    {Stratio BD} % Organization
    {Madrid, Spain} % Location
    {2017 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Orchestrated dynamic team-building events to cultivate synergy and morale among staff.}
        \item {Designed cutting-edge training programs fostering professional growth and honing essential soft skills, empowering individuals for success in a rapidly evolving workplace.}
        \item {Specialized in fostering happiness and professional development.}
        \item {Implemented engagement strategies and promoted a positive work environment.}
        \item {Designed and managed Diversity, Equity, and Inclusion (DEI) strategies.}
        \item {Implemented strategies to enhance employee engagement and well-being.}
        \item {Played a key role in promoting a positive work environment conducive to innovation and growth}
      \end{cvitems}
    }

   \cventry
    {People Care and Well-being Consultant} % Job title
    {The Corporate Wellbeing} % Organization
    {Madrid, Spain} % Location
    {2014 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented transformation plans to improve working environments.}
      \end{cvitems}
    }


   \cventry
    {HR Senior Consultant} % Job title
    {Humanlab} % Organization
    {Madrid, Spain} % Location
    {2009 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed sales and commercial operations.}
        \item {Designed methodology and executed projects in recruiting, engagement, training \& reskilling, performance, professional coaching, and change management.}
      \end{cvitems}
    }

   \cventry
    {International Recruiter} % Job title
    {Airbus} % Organization
    {Madrid, Spain} % Location
    {2008 - 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and executed talent acquisition assessments.}
      \end{cvitems}
    }

   \cventry
    {HR Generalist} % Job title
    {Shell} % Organization
    {Madrid, Spain} % Location
    {2006 - 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed recruiting, HR advisory, training, diversity, and inclusiveness.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
